---
format: 
  pdf:
    pdf-engine: lualatex
    documentclass: article
    fontsize: 11pt
    mainfont: "Arial"        # font family
    include-in-header: header.tex
geometry:
  - a4paper
  - left=1cm
  - right=1.5cm
  - top=1.5cm
  - bottom=0.5cm
params:
  pt_vorname: NULL
  pt_name: NULL
  pt_praxis: NULL
  pt_adresse: NULL
  pt_plz: NULL
  pt_ort: NULL
  pt_tel: NULL
  pt_mail: NULL
  pt_zsr: NULL
  pt_knr: NULL
  pt_emfit: NULL
  pt_pilat_nr: NULL
  abo_type: NULL
  abo_start: NULL
  abo_end: NULL
  abo_price: NULL
  mem_kk: NULL
  mem_zv: NULL
  mem_vnr: NULL
  mem_name: NULL
  mem_vorname: NULL
  mem_adresse: NULL
  mem_plz: NULL
  mem_mail: NULL
---

# Gesundheitsförderung / Präventions-Training 2024

Dieses Formular bestätigt, dass die versicherte Person ein gesundheitsförderndes Training bei einem \
PilatesCare Anbieter besucht hat.


```{r echo=FALSE, warning=FALSE, message=FALSE}
# libraries
library(flextable)
library(officer)
library(dplyr)

# define a theme that will be used for all flextables
my_theme <- function(x, ...) {
  std_border <- fp_border(width = 1, color = "black") 
  
  x <- x |> 
    font(part = "all", fontname = "Arial") |> 
    fontsize(part = "body", size = 11) |> # make text in cells 11pt
    fontsize(part = "header", size = 12) |> # make text in header 12pt
    bold(part = "header") |>  # make text in header bold
    bg(bg = "gray70", part = "header") |>  # grey background in header
    border_remove() |> 
    border_outer(part= "all", border = std_border) # make outer border

  x
}

# define a theme that an empty line should be drawn if the parameter is empty
field_or_line <- function(value, line_width = 40) {
  if (is.null(value) || value == " " || value == "") {
    paste(rep("_", line_width), collapse = "")
    # paste0("\n", paste(rep("_", line_width), collapse = ""))  # newlines add padding
  } else {
    value
  }
}
# field_or_line <- function(value, line_width = 60) {
#   if (is.null(value) || value == " " || value == "") {
#     paste0("\n", paste(rep("_", line_width), collapse = ""))
#   } else {
#     paste0("\n", value)  # pad all values, not just lines
#   }
# }

# construct data for the first table
data <- data.frame(
  col1 = c("Name", "Vorname", "Praxis", "Adresse", "PLZ/Ort", "Tel.", "E-Mail"),
  col2 = c(params$pt_name, params$pt_vorname, params$pt_praxis, params$pt_adresse, paste(params$pt_plz, params$pt_ort), params$pt_tel, params$pt_mail),
  col3 = c("ZSR-Nummer", "K-Nummer", "EMfit-Nummer", "", "", "", ""),
  col4 = c(params$pt_zsr, params$pt_knr, params$pt_emfit, "", "", "", "")
  )

# construct the flextable
ft <- flextable(data)
ft <- set_header_labels(ft, 
                        col1 = "Anbieter", 
                        col2 = "",
                        col3 = paste("PilatesCare Mitglieder-Nr.:", params$pt_pilat_nr),
                        col4 = "")

# apply the theme
ft <- my_theme(ft)

# merge col3 and col4 in header
ft <- merge_at(ft, i = 1, j = 3:4, part = "header") 

# set fixed width
ft <- set_table_properties(
  ft,
  layout = "fixed",
  width = 1
)

# define widths -> total width 18cm
ft <- width(ft, j = 1, width = 2, unit = "cm")
ft <- width(ft, j = 2, width = 8, unit = "cm")
ft <- width(ft, j = 3, width = 3, unit = "cm")
ft <- width(ft, j = 4, width = 5, unit = "cm")

# return flextable
ft
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# build a switch that defines if checkboxes should be filled or not based on abo_type
checked <- switch(
  as.character(params$abo_type),
  "10" = c(TRUE, FALSE, FALSE),
  "3"  = c(FALSE, TRUE, FALSE),
  "6"  = c(FALSE, FALSE, TRUE),
  c(FALSE, FALSE, FALSE)
)

# build the data for table
data <- data.frame(
  col1 = c("", "Abo-Beginn:", "Preis: CHF", "Für die Qualitätskontrolle kann sich die Krankenkasse bei PilatesCare erkundigen, ob der oben erwähnte \nAnbieter die Voraussetzung als PilatesCare REHA-TrainerIn erfüllt. www.pilatescare.ch / info@pilatescare.ch"),
  col2 = c("", params$abo_start, params$abo_price, ""),
  col3 = c("", "Abo-Ende:", "", ""),
  col4 = c("", params$abo_end, "", "")
)

# build flextable
ft <- flextable(data)
ft <- set_header_labels(ft,
                        col1 = "Kurs PilatesCare Training",
                        col2 = "",
                        col3 = "",
                        col4 = "")

# replace the first cell of the flextable with three checkboxes based on the switch
ft <- compose(
  ft,
  i = 1,
  j = 1,
  value = as_paragraph(
    
    as_chunk(
      ifelse(checked[1], "■", "□"),
      props = fp_text(font.size = 16)
    ),
    " 10er-Abo    ",
    
    as_chunk(
      ifelse(checked[2], "■", "□"),
      props = fp_text(font.size = 16)
    ),
    " 3-Monats-Abo    ",
    
    as_chunk(
      ifelse(checked[3], "■", "□"),
      props = fp_text(font.size = 16)
    ),
    " 6-Monats-Abo"
  )
)

# apply the previously defined theme for the flextable
ft <- my_theme(ft)

# merge col 1-4 in header
ft <- merge_at(ft, i = 1, j = 1:4, part = "header")

# merge col 1-4 in row 1
ft <- merge_at(ft, i = 1, j = 1:4, part = "body")

# merge col 1-4 in row 4
ft <- merge_at(ft, i = 4, j = 1:4, part = "body")

# make text smaller in row 4
ft <- fontsize(ft, i = 4, j = 1, size = 10, part = "body")

# set fixed width
ft <- set_table_properties(
  ft,
  layout = "fixed",
  width = 1
)

# define widths -> total width 18cm
ft <- width(ft, j = 1, width = 3, unit = "cm")
ft <- width(ft, j = 2, width = 4, unit = "cm")
ft <- width(ft, j = 3, width = 3, unit = "cm")
ft <- width(ft, j = 4, width = 8, unit = "cm")

# return flextable
ft
```



```{r echo=FALSE, warning=FALSE, message=FALSE}
# build the data for the third table
data <- data.frame(
  col1 = c("Name der Krankenkasse", "Zusatzversicherung", "Versicherungs-Nummer", "Name", "Vorname", "Adresse", "PLZ/Ort", "E-Mail"),
  col2 = c(
    field_or_line(params$mem_kk),
    field_or_line(params$mem_zv),
    field_or_line(params$mem_vnr),
    field_or_line(params$mem_name),
    field_or_line(params$mem_vorname),
    field_or_line(params$mem_adresse),
    field_or_line(params$mem_plz),
    field_or_line(params$mem_mail)
  )
)

# build flextable
ft <- flextable(data)
ft <- set_header_labels(ft,
                        col1 = "Versicherte Person",
                        col2 = ""
                        )
# apply theme
ft <- my_theme(ft)

# merge col1 and col2 in header
ft <- merge_at(ft, i = 1, j = 1:2, part = "header")

# set fixed width
ft <- set_table_properties(
  ft,
  layout = "fixed",
  width = 1
)

# define widths -> total width 18cm
# note: somehow, 18cm seems to be a bit small with only two columns (maybe because of col seperators?) -> that's why I used total width of 18.3cm here
ft <- width(ft, j = 1, width = 5, unit = "cm")
ft <- width(ft, j = 2, width = 13.3, unit = "cm")

# return flextable
ft
```

Ort und Datum: `r params$pt_ort`, `r format(Sys.Date(), "%d.%m.%Y")`

\begin{multicols}{2}

Unterschrift Anbieter \\
\includegraphics[width=6.5cm]{`r paste0("../signatures/therapist_signatures/signed_line_", params$pt_vorname, ".png")`}

\columnbreak

Unterschrift versicherte Person \\
\includegraphics[width=6.5cm]{"../signatures/unsigned_line.png"}

\end{multicols}
